Seismic parameter estimation and the Canadian crust

### 2013-02-01 paper/draftBP.tex
test wavelet thresholding on RFs write a little more

%% -----------------------------------------------%%
\section{Data and method}
   Seismic data utilized in this study comes from 343 stations across Canada from all available networks. Of these stations 146 were used for analysis. All stations are broadband with data being used between the years 2000 and 2012. Receiver function analysis has been widely employed over many years to investigate the earths structure.
   Two derivations have been used in this study, one well tested stacking approach (Zhu and Kanamori, 2000) and the other a recent method that has not been employed at scale (Bostock, 2010). Both methods rely on the fact that the incoming S-wave contains energy from the direct arrival as well as reflected phases resulting from sharp velocity contrasts. Deconvolution of the P-wave energy arrival, used as an estimate for the source function, from the S-wave signal produces a Green's function with energy peaks at the times of the main and reflected arrivals. For better separation of P and S wave energy all components are rotated into radial and transverse dimensions and transformed into P, SV and SH components with a wave field decomposition transfer matrix (Bostock, 1998).
   Deconvolution is performed by minimizing the general cross validation function $GCV(\delta)$ where $\delta$ is used the regularizer (Bostock, 1998; Golub et al., 1979). This method is an $L_2$ frequency domain deconvolution which performs quickly and makes no assumptions on the noise in the data. All deconvolved signals are filtered between 0.04hz and 3.0hz and are stacked with weights $w_1=0.5$, $w_1=0.3$, $w_1=0.2$ for the Ps, PpPs and PpSs phases respectively.

   <Error Calculations>

@@

%% -----------------------------------------------%%
\section{Results}
<Results go here>

>>>>

%% -----------------------------------------------%%
\section{Data and method}
   Seismic data utilized in this study comes from 343 stations across Canada from all available networks. Of these stations 146 were used for analysis. All stations are broadband with data being used between the years 2000 and 2012. Receiver function analysis has been widely employed over many years to investigate the earths structure.
   Two derivations have been used in this study, one well tested stacking approach (Zhu and Kanamori, 2000) and the other a recent method that has not yet been employed at scale (Bostock, 2010). Both methods rely on the fact that the incoming S-wave contains energy from the direct arrival as well as reflected phases resulting from sharp velocity contrasts. Deconvolution of the P-wave energy arrival, used as an estimate for the source function, from the S-wave signal produces a Green's function with energy peaks at the times of the main and reflected arrivals. For better separation of P and S wave energy all components are rotated into radial and transverse dimensions and transformed into P, SV and SH components with a wave field decomposition transfer matrix (Bostock, 1998).
   Deconvolution is performed by minimizing the general cross validation function $GCV(\delta)$ where $\delta$ is used the regularizer (Bostock, 1998; Golub et al., 1979). This method is an $L_2$ frequency domain deconvolution which performs quickly and makes no assumptions on the noise in the data. All deconvolved signals are filtered between 0.04hz and 3.0hz and are stacked with weights $w_1=0.5$, $w_1=0.3$, $w_1=0.2$ for the Ps, PpPs and PpSs phases respectively. Error calculations are performed with bootstrap resampling by rerunning the processing with randomly chosen receiver functions - allowing multiples - 1024 times. The error is obtained by taking the standard deviation of the results.

@@

%% -----------------------------------------------%%
\section{Results}
Canada data

Data across geological provinces

Archean versus Proterozoic
